---
title: "p8105_hw3_jc4166"
author: "Jerri Chen"
date: "2019-10-04"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```

## Problem 1
```{r}
library(p8105.datasets)
data("instacart")
instacart_data = instacart
```
Instagart is a dataset that contains `r ncol(instacart_data)` variables and `r nrow(instacart_data)` entries describing Instacart customer orders, which are grocery store orders placed online. Each entry represents a single order, and includes information on the user who ordered, the day of week and hour of day when the item was ordered, the order in which the item was added to their cart, and information that categorizes the product into departments and aisles.

- Explore the data:
- I am interested in what the most popular day of the week to place orders is.
```{r}
instacart_data %>% 
  select("order_dow") %>% 
  mutate(order_dow = case_when(
      order_dow == "0" ~ "Sunday",
      order_dow == "1" ~ "Monday",
      order_dow == "2" ~ "Tuesday",
      order_dow == "3" ~ "Wednesday",
      order_dow == "4" ~ "Thursday",
      order_dow == "5" ~ "Friday",
      order_dow == "6" ~ "Saturday")
    ) %>% 
  count(order_dow, name = "n_dow") %>% 
  arrange(desc(n_dow))
```
The most popular day of week for placing orders is Sunday.

- What time on Sundays are people placing orders?
```{r}
instacart_data %>% 
  filter(order_dow == "0") %>% 
  select(order_hour_of_day) %>% 
  count(order_hour_of_day, name = "n_hour") %>% 
  arrange(desc(n_hour))
```
The most popular time of day on Sunday to place an order is 2:00 PM, and the top three hours are 1:00, 2:00, and 3:00 PM.

- How many aisles are there, and which aisles are the most items ordered from?
```{r message = FALSE}
instacart_aisle = instacart_data %>%
  select(aisle, aisle_id) %>% 
  count(aisle, aisle_id, name = "n_aisle") %>% 
  arrange(desc(n_aisle))
```
There are `r nrow(instacart_aisle)` aisles. The "fresh vegetables" aisle has the most orders, followed by "fresh fruits" and "packaged vegetables fruits."

- Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart_data %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n, .desc = FALSE)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
    coord_flip() + 
	  geom_bar(stat = "identity") + 
    labs(
      title = "Number of Items Ordered From Each Aisle", 
      x = "Aisle Name ", 
      y = "Number of Orders"
      )
```

- Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r message = FALSE}
instacart_data %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(n = n()) %>% 
  top_n(3) %>% 
  arrange(desc(n)) %>% 
  knitr::kable(caption = 'Most Popular Items by Aisle')
```

In packaged vegetables and fruits, the three most popular items are organic baby spinach, organic raspberries, and organic blueberries. In baking ingredients, the three most popular items are light brown sugar, pure baking soda, and cane sugar. In dog food care, the three most popular items are snack sticks, organix chicken & brown rice, and small dog biscuits.

- Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r message = FALSE}
instacart_data %>% 
    select(product_name, order_dow, order_hour_of_day) %>%
    filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
    group_by(product_name, order_dow) %>%
    summarize(mean_hour = round(mean(order_hour_of_day))) %>%
    mutate(order_dow = case_when(
      order_dow == "0" ~ "Sunday",
      order_dow == "1" ~ "Monday",
      order_dow == "2" ~ "Tuesday",
      order_dow == "3" ~ "Wednesday",
      order_dow == "4" ~ "Thursday",
      order_dow == "5" ~ "Friday",
      order_dow == "6" ~ "Saturday")
    ) %>%
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hour") %>%
  rename("Product Name" = product_name) %>% 
  knitr::kable(caption = 'Mean Hour of Day for Product Orders Each Day of the Week')
```

## Problem 2
```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

```{r}
brfss_smart2010_data = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health")
```

