---
title: "p8105_hw3_jc4166"
author: "Jerri Chen"
date: "2019-10-04"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```

## Problem 1
```{r}
library(p8105.datasets)
data("instacart")
instacart_data = instacart
```
Instagart is a dataset that contains `r ncol(instacart_data)` variables and `r nrow(instacart_data)` entries describing Instacart customer orders, which are grocery store orders placed online. Each entry represents a single order, and includes information on the user who ordered, the day of week and hour of day when the item was ordered, the order in which the item was added to their cart, and information that categorizes the product into departments and aisles.

- Explore the data:
- I am interested in what the most popular day of the week to place orders is.
```{r}
instacart_data %>% 
  select("order_dow") %>% 
  mutate(order_dow = case_when(
      order_dow == "0" ~ "Sunday",
      order_dow == "1" ~ "Monday",
      order_dow == "2" ~ "Tuesday",
      order_dow == "3" ~ "Wednesday",
      order_dow == "4" ~ "Thursday",
      order_dow == "5" ~ "Friday",
      order_dow == "6" ~ "Saturday")
    ) %>% 
  count(order_dow, name = "n_dow") %>% 
  arrange(desc(n_dow))
```
The most popular day of week for placing orders is Sunday.

- What time on Sundays are people placing orders?
```{r}
instacart_data %>% 
  filter(order_dow == "0") %>% 
  select(order_hour_of_day) %>% 
  count(order_hour_of_day, name = "n_hour") %>% 
  arrange(desc(n_hour))
```
The most popular time of day on Sunday to place an order is 2:00 PM, and the top three hours are 1:00, 2:00, and 3:00 PM.

- How many aisles are there, and which aisles are the most items ordered from?
```{r message = FALSE}
instacart_aisle = instacart_data %>%
  select(aisle, aisle_id) %>% 
  count(aisle, aisle_id, name = "n_aisle") %>% 
  arrange(desc(n_aisle))
```
There are `r nrow(instacart_aisle)` aisles. The "fresh vegetables" aisle has the most orders, followed by "fresh fruits" and "packaged vegetables fruits."

- Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart_data %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n, .desc = FALSE)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
    coord_flip() + 
	  geom_bar(stat = "identity") + 
    labs(
      title = "Number of Items Ordered From Each Aisle", 
      x = "Aisle Name ", 
      y = "Number of Orders"
      )
```

- Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r message = FALSE}
instacart_data %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarize(n = n()) %>% 
  top_n(3) %>% 
  arrange(desc(n)) %>% 
  knitr::kable(caption = 'Most Popular Items by Aisle')
```

In packaged vegetables and fruits, the three most popular items are organic baby spinach, organic raspberries, and organic blueberries. In baking ingredients, the three most popular items are light brown sugar, pure baking soda, and cane sugar. In dog food care, the three most popular items are snack sticks, organix chicken & brown rice, and small dog biscuits.

- Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r message = FALSE}
instacart_data %>% 
    select(product_name, order_dow, order_hour_of_day) %>%
    filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
    group_by(product_name, order_dow) %>%
    summarize(mean_hour = round(mean(order_hour_of_day))) %>%
    mutate(order_dow = case_when(
      order_dow == "0" ~ "Sunday",
      order_dow == "1" ~ "Monday",
      order_dow == "2" ~ "Tuesday",
      order_dow == "3" ~ "Wednesday",
      order_dow == "4" ~ "Thursday",
      order_dow == "5" ~ "Friday",
      order_dow == "6" ~ "Saturday")
    ) %>%
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hour") %>%
  rename("Product Name" = product_name) %>% 
  knitr::kable(caption = 'Mean Hour of Day for Product Orders Each Day of the Week')
```

## Problem 2
```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

```{r}
brfss_smart2010_data = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  rename(
    "state" = locationabbr,
    "county" = locationdesc
         ) %>% 
  filter(topic == "Overall Health") %>% 
  filter(response == c("Poor", "Fair", "Good", "Very Good", "Excellent")) %>% 
  mutate(response = as.factor(response))
```

- In 2002, which states were observed at 7 or more locations?
```{r}
brfss_smart2010_data %>% 
  filter(year == "2002") %>% 
  distinct(state, county) %>% 
  count(state) %>% 
  filter(n >= 7)
```
In 2002, the states NJ, MA, and PA were observed at 7 or more locations.

- What about in 2010?
```{r}
brfss_smart2010_data %>% 
  filter(year == "2010") %>% 
  distinct(state, county) %>% 
  count(state) %>% 
  filter(n >= 7)
```
In 2010, the states CA, CO, FL, MA, MD, NC, NE, NJ, NY, OH, TX, and WA were observed in 7 or more locations.

- Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).
```{r}
brfss_excellent = brfss_smart2010_data %>% 
  filter(response == "Excellent") %>% 
  select("year", "state", "data_value") %>% 
  group_by(year, state) %>% 
  summarize(avg_data_value = mean(data_value, na.rm = TRUE))%>% 
  drop_na()

brfss_excellent %>% 
  ggplot(aes (x = year, y = avg_data_value, color = state)) + 
  geom_point() + 
  geom_line() + 
  labs(
    title = "Average Data Value Over Time for 'Excellent' Responses", 
    x = "Year", 
    y = "Average Data Value")
```

- Make a two-panel plot showing, for the years 2006 and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.
```{r}
brfss_ny = brfss_smart2010_data %>% 
  filter(state == "NY") %>% 
  filter(year == c("2006", "2010")) %>% 
  select("year", "county", "response", "data_value")

brfss_ny %>% 
  ggplot(aes(x = data_value, fill = response)) + 
  geom_density(alpha = .4) + 
  facet_grid(~year) +
  labs(
      title = "Distribution of Data Value By Response for 2006 and 2010",
      x = "Response",
      y = "Data Values")
```

## Problem 3
This data set has 5 weeks worth of accelerometer data from a 63 year old man with congestive heart failure. The data has been tidied, and includes the following variables: week (1-5), day (Monday - Sunday), day_type (weekday or weekend), hour_of_day (0-23), minute_of_day (1-1440), and activity_counts, which counts the activities that occured during the corresponding minute of day. Since it includes 5 weeks of continuous 24-hour-a-day recordings, one would expect 5 weeks x 7 days a week x 1440 minutes a day = 50,400 obersations, which is the exact number of entries in the data set. 

```{r}
accel_data = read_csv("./data/accel_data.csv") %>% 
  janitor:: clean_names() %>% 
  mutate(day_type = ifelse(day %in% c("Saturday", "Sunday"), "weekend", "weekday")) %>%
  pivot_longer(
  activity_1:activity_1440, 
  names_to = "minute", 
  names_prefix = "activity_", 
  values_to = "activity_counts")%>% 
  mutate(minute_of_day = as.numeric(minute)) %>% 
  mutate(hour_of_day = as.integer(minute_of_day/60)) %>% 
  select("week", "day", "day_type", "hour_of_day", "minute_of_day", "activity_counts")
```

I tried to order the "day" variable using the following code within the above code chunk and it seemed to do nothing:
mutate(day = as.factor(day)) %>% 
  group_by(week) %>% 
  mutate(day = ordered(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) %>%


- The following table show the average total activity count per day of week for the duration of the study. Saturday has the lowest activity count, and Friday the highest.
```{r}
accel_data %>% 
  group_by(day) %>% 
  summarize(total_activity = mean(activity_counts)) %>% 
  knitr::kable(caption = 'Average Activity Count Per Day of Week')
```

- The following graph shows the 24-hour activity time courses for each day of the week. Overall, the majority of activity occurs between 5am and 8pm, with a decrease around lunch time (as might be expected). It is possible he may participate in some kind of activity that increases his physical activity at certain times of week; for example, he has a lot of activity on Wednesday evenings and Sunday mornings. The day of the week that seems to have overall the lowest activity count throught the day is Tuesday.
```{r}
accel_data %>%
  ggplot(aes(x = hour_of_day, y = activity_counts, color = day)) + 
  geom_line() + 
  labs(
    title = "Activity Counts Over 24 Hour Period",
    x = "Hour of Day",
    y = "Activity Count")
```

